Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-03-26 document/ms.tex
starting figures and various paper things

%
%  RULES OF THE GAME, MOTHAFUCKERS.
%
%  * 80 characters
%  * line breaks at the ends of sentences
%  * that is all.
%

@@

\acknowledgments
It is a pleasure to thank
    Erik Petigura (Berkeley),
    \ldots
for helpful contributions to the ideas and code presented here.
This project was partially supported by the NSF (grant AST-0908357), and NASA
(grant NNX08AJ48G).

\section{Results}

@@

>>>>

%
%  RULES OF THE GAME, MOTHAFUCKERS.
%
%  * 80 characters
%  * line breaks at the ends of sentences
%  * eqnarrys ONLY
%  * that is all.
%

@@

\section{Separable Distribution}

The first model that we consider for $\rate(\period,\,\radius)$ is a simple
separable distribution.
This assumption means that the rate can be written as
\begin{eqnarray}
\rate(\period,\,\radius) &=& \rate(\period)\,\rate(\radius)
\end{eqnarray}
and, more specifically, we model the period distribution as a broken power law
\dfmtodo{CHECK ME!!}
\begin{eqnarray}
\rate(\period) &\propto& \frac{\period^\alpha \,
(\period+\period_0)^{\beta-\alpha}}{\period_0^\beta}
\end{eqnarray}
and the radius distribution as a piecewise constant function (or histogram)
where the parameters are the bin heights.

@@

\acknowledgments
It is a pleasure to thank
    \ldots
for helpful contributions to the ideas and code presented here.
This project was partially supported by the NSF (grant AST-0908357), and NASA
(grant NNX08AJ48G).
